Methods for Analyzing Models of\\ Rod-Shaped Bacteria

### 2025-09-25 paper/main.tex
fill description of figure

\begin{figure}
    \centering
    \begin{tikzonimage}[width=0.32\textwidth]
        {docs/source/_static/fitting-methods/extract_positions-004000.png}
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{A}};
    \end{tikzonimage}
    \begin{tikzonimage}[width=0.32\textwidth]
        {docs/source/_static/fitting-methods/extract_positions-006000.png}
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{B}};
    \end{tikzonimage}
    \begin{tikzonimage}[width=0.32\textwidth]
        {docs/source/_static/fitting-methods/extract_positions-008000.png}
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{C}};
    \end{tikzonimage}
    \begin{tikzonimage}[width=0.5\textwidth]
        {docs/source/_static/fitting-methods/displacement-calculations.png}%
        \node at (0.03, 0.99)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{D}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.5\textwidth]
        {docs/source/_static/fitting-methods/displacement-distribution.png}
        \node at (0.03, 0.99)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{E}};
    \end{tikzonimage}
    \caption{
        Progression of generated masks with estimated and exact positions.
        Comparison of masks across generations. Compare estimated with exact rod lengths.
"Iceberg plot"
    }
    \label{fig:benchmarking-extraction-algorithm}
\end{figure}

>>>>

\begin{figure}
    \centering
    \begin{tikzonimage}[width=0.32\textwidth]
        {docs/source/_static/fitting-methods/extract_positions-004000.png}
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{A}};
    \end{tikzonimage}
    \begin{tikzonimage}[width=0.32\textwidth]
        {docs/source/_static/fitting-methods/extract_positions-006000.png}
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{B}};
    \end{tikzonimage}
    \begin{tikzonimage}[width=0.32\textwidth]
        {docs/source/_static/fitting-methods/extract_positions-008000.png}
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{C}};
    \end{tikzonimage}
    \begin{tikzonimage}[width=0.5\textwidth]
        {docs/source/_static/fitting-methods/displacement-calculations.png}%
        \node at (0.03, 0.99)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{D}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.5\textwidth]
        {docs/source/_static/fitting-methods/displacement-distribution.png}
        \node at (0.03, 0.99)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{E}};
    \end{tikzonimage}
    \caption{
        Subfigures (A-C) show rendered masks of a simulation where the extracted positions have been
        drawn within the individual agents.
        Subfigure (D) displayes the average rod length of the exact and extracted data.
        The light blue region is the mean distance between vertices of extracted and exact
        positions which captures the inherent uncertainty of our method.
        Subfigure (E) displays all of these distances on a logarithmic scale.
        The colorscale represents earlier (darker) and later (brighter) temporal states of our
        simulation.
        Overall, this plot shows a widening of the distance distributions for increasing simulation
        times.
    }
    \label{fig:benchmarking-extraction-algorithm}
\end{figure}
